---
title: "HW1_stat"
author: "Anna Rusnak"
date: "05 04 2022"
output: html_document
---
```{r}
library(ggplot2)
```

```{r}
num_Trials <- 10^7
```

# fix the seed to have reproductive results 
```{r}
set.seed(2022)
```

# sample x from a uniform distribution
```{r}
x <- runif(num_Trials, min = -pi/2, max = pi/2)
```


# sample y from a uniform distribution
```{r}
y_min <- -pi
y_max <- 1
y <- runif(num_Trials, min = y_min, max = y_max)
```
# The answer will be : number of points inside / total points = area inside / total area 

### If a point is inside that means: 
### 1) y > - 2*x - pi 
### 2) y > 2*x - pi
### 3) y < -sin(2*x) when x >= pi/2 and < 0 
### 4) y < sin(2*x) when x >= 0 and <= pi/2 
```{r}
is_inside <- (y > - 2*x - pi) & 
              (y > 2*x - pi) & 
              (((y < -sin(2*x)) & x < 0 ) |  
              ((y < sin(2*x)) & x >= 0 )  )
```

### The number of points inside / total points
```{r}
ratio_inside <- sum(is_inside) / num_Trials
ratio_inside
```

```{r}
total_area_rect <- pi * (y_max - y_min)
total_area_rect
```

```{r}
area_inside <- total_area_rect * ratio_inside
area_inside
```

```{r}
df <- data.frame(x=x, y=y, is_inside=is_inside)
ggplot(df, aes(x, y)) + 
  geom_point(aes(color=is_inside)) + 
  theme_bw()
```